\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-01 metatheory-condensed.tex
singleton type

@@

We illustrate this with \cref{fig:stlc-linkage-typing}.
On the left is code excerpted from \cref{fig:stlc-mechanized}, and on the right
is how the corresponding fields are modeled and typed in \TT.
%
$\lkg_i$ is the linkage that adds the $i$-th field~$t_i$ with the typing
$\goodTerm{A_i}{t_i}{T_i}$.
%
For readability, we feel free to use a notation with explicit names
in this typing judgment:
we name the context as $\mathit{self}$ (cf.~\cref{fig:stlc-compiled})
and feel free to write its type, which is a dependent tuple type, as a
dependent record type with labels.
%
\begin{itemize}[labelsep=*,leftmargin=1pc]

@@

\item
By contrast, $\wsig_{\texttt{tm}}$ is hidden from the typing context of all other fields.
Their typing depends on the knowledge that \lsti!tm! has type~$\cU$,
rather than \TyS{\wcode{\wsig_{\texttt{tm}}}},
so they can be reused in a context where \lsti!tm! is defined as $\wcode{\wsig'_{\texttt{tm}}}$,
where $\wsig'_{\texttt{tm}}$ extends~$\wsig_{\texttt{tm}}$ with additional constructors.

>>>>

A singleton type $\TyS{t}$ helps expose the definition of a term~$t$
in its type (rule \ruleref{tm/s})~\cite{aspinall1995singleton,stone2000}.

@@

We illustrate this with \cref{fig:stlc-linkage-typing}.
On the left is code excerpted from \cref{fig:stlc-mechanized}, and on the right
is how the corresponding fields are modeled and typed in \TT.
%
$\lkg_i$ is the linkage that adds the $i$-th field~$t_i$ with the typing
$\goodTerm{A_i}{t_i}{T_i}$.
%
For readability, we feel free to use a notation with explicit names
in this typing judgment:
we name the context as $\mathit{self}$ (cf.~\cref{fig:stlc-compiled})
and feel free to write its type, which is a dependent tuple type, as a
dependent record type with labels.
%
\begin{itemize}
  [leftmargin=4ex]
  %[labelsep=*,leftmargin=1pc]

@@

\item
By contrast, $\wsig_{\texttt{tm}}$ is hidden from the typing context of all other fields.
Their typing depends on the knowledge that \lsti!tm! has type~$\cU$,
rather than \TyS{\wcode{\wsig_{\texttt{tm}}}},
so they can be reused in a context where \lsti!tm! is defined as $\wcode{\wsig'_{\texttt{tm}}}$,
where $\wsig'_{\texttt{tm}}$ extends~$\wsig_{\texttt{tm}}$ with additional constructors.
%
For example, in \cref{fig:stlc-linkage-typing}, the typing of the case handlers of
\lsti{subst} is agnostic of the definition of \lsti!tm!---it sees only $\text{\lsti!tm!}:\cU$---so
they can be reused by a linkage modeling \lsti{STLCFix}.
